\gettitle

### 2019-12-12 assignment4/submission4.tex
Added exercise 4.3

>>>>

\begin{itemize}
    \item[\(H_1\):] could be generated by 2-phase-locking. The shrinking phase for each transaction begins right after the last operation before the commit.

        Execution split for each resource:

        \begin{itemize}
            \item[\(y\):] \(rL_1 \rightarrow r_1 \rightarrow wL_1 \rightarrow w_1 \rightarrow wU_1 \rightarrow rL_2 \rightarrow r_2 \rightarrow c_1 \rightarrow rU_2 \rightarrow c_2 \rightarrow c_3\)
            \item[\(x\):] only read operations $\Rightarrow$ no conflicting locks possible
            \item[\(z\):] only read operations $\Rightarrow$ no conflicting locks possible
            \item[\(w\):] \(c_1 \rightarrow wL_2 \rightarrow w_2 \rightarrow wU_2 \rightarrow c_2 \rightarrow wL_3 \rightarrow w_3 \rightarrow wU_3 \rightarrow c_3\)
        \end{itemize}

    \item[\(H_2\):] is not possible with 2-phase-locking!

        Conflicting excerpt: \(r_1[x] \rightarrow w_2[x] \rightarrow r_1[y]\)

        Either \(T_2\) cannot aquire the write lock for \(w_2[x]\) as \(T_1\) still holds the read lock or \(T_1\) is already in the lock shrinking phase when it wants to execute \(r_1[y]\) (this is the first operation of \(T_1\)on \(y\)) but both transactions commit.

    \item[\(H_3\):] is not possible with 2-phase-locking!

        Conflicting excerpt: \(r_1[y] \rightarrow w_3[y] \rightarrow w_1[z]\)

        Analog situation to \(H_2\). Shrinking for \(T_1\) can only happen after \(w_1[z]\) but \(r_1[y]\) and \(w_3[y]\) are conflicting locks.

\end{itemize}
